---
title: "Data Science Center attendance_lists data"
author: 'Ian May UID: 304663145'
date: "December 4, 2018"
output: html_document
---

```{r setup, warning=FALSE}
library(RCurl)
library(dplyr)
library(ggplot2)
library(ggthemes)
attend <- getURL("https://docs.google.com/spreadsheets/d/e/2PACX-1vTxBxubeoxL0jjD0RuPasdhmzhOHXzheJT_U9_UWAQqTdL1fnuaBy1b1J8pPXyCeq-IslHeQepuLyMC/pub?gid=983795958&single=true&output=csv")
attend <- read.csv(textConnection(attend))
```

```{r name changes}
attend[attend==""] <- NA
attend$event[attend$event == "Introducing Los Angeles Region Imagery Acquisition Consortium (LARIAC) Program at UCLA"] <- "Introducing LARIAC Program at UCLA"
attend$event[attend$event == "Faculty Development Workshop: Teaching Transparent Methods of Empirical Research"] <- "Faculty Development: Methods of Empirical Research"
attend$role[attend$role == "staff "] <- "staff"
```

```{r event attendance}
attend %>% 
  group_by(event, practice_topic, role) %>% 
  summarize(number_people = n()) %>% 
  ggplot(aes(x=event, y=number_people, fill = role)) + 
    geom_col()+ theme(axis.text.x = element_text(angle = 45, size = 10, hjust = 1)) +labs(title = "Total Attendance Per Event", x= "Event Name", y="Attendance", fill = "Role")
```

{Code for pyramid plot (not complete)}
 X Axis Breaks and Labels 
brks <- seq(-15000000, 15000000, 5000000)
lbls = c(seq(15, 0, -5), seq(5, 15, 5))

 Plot
attend %>% 
  group_by(event, practice_topic, role) %>% 
  summarize(number_people = n()) %>% 
ggplot(email_campaign_funnel, aes(x = role, y = number_people, fill = Gender)) +   # Fill column
                              geom_bar(stat = "identity", width = .6) +   # draw the bars
                              scale_y_continuous(breaks = brks,   # Breaks
                                                 labels = lbls) + # Labels
                              coord_flip() +  # Flip axes
                              labs(title="Email Campaign Funnel") +
                              theme_tufte() +  # Tufte theme from ggfortify
                              theme(plot.title = element_text(hjust = .5), 
                                    axis.ticks = element_blank()) +   # Centre plot title
                              scale_fill_brewer(palette = "Dark2")  # Color palette


```{r Attendance per date}
attend %>% 
  group_by(date, event, practice_topic) %>% 
  summarize(number_date = n()) %>% 
   ggplot(aes(x=date, y=number_date, fill= practice_topic)) + 
    geom_col()+ theme(axis.text.x = element_text(angle = 45, size = 10, hjust = 1)) + labs(title = "Total Attendance Per Date", x = "Date", y="Attendance")
```

{Code for R Date line graph , not complete}
attend %>% 
  group_by(date, event, practice_topic) %>% 
  summarize(number_date = n()) %>% 
  ggplot(aes_(x=date, y=number_date)+
           geom_line())
  

  theme(axis.text.x = element_text(angle = 45, size = 10, hjust = 1)) + labs(title = "Total Attendance Per Date", x = "Date", y="Attendance")



```{r Attendance per Role}
attend %>% 
  group_by(role) %>% 
  summarize(number_role = n()) %>% 
   ggplot(aes(x=reorder(role, -number_role), y=number_role)) + 
    geom_col()+ theme(axis.text.x = element_text(angle = 45, size = 10, hjust = 1)) + labs(title = "Total Attendance Per Role", x = "Role", y="Attendance") +geom_text (aes(label=number_role), vjust= -0.5)
```


